Irt plot extra

### 2023-01-03 manuscript_v2.Rmd
EFA univariate and multivariate

**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001). The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

>>>>

**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`). Likewise, our data violated the both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions ([@mardiaMeasuresMultivariateSkewness1970]; multivariate skew=`r printnum(mardia$b1p)`, p<0.001; multivariate kurtosis= `r printnum(mardia$b2p)`,p <0.001). The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.
